Age modifies the effect of total cholesterol level on systolic blood pressure: Analysis of evidence from the 2015 - 2018 NHANES data

### 2023-12-12 manuscript/paper.Rmd
up

---
title: "Workday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population"
thanks: "Replication files are available on the author's Github account (http://github.com/okutse/sleepBP). **Current version**: `r format(Sys.time(), '%B %d, %Y')`"
#subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Monic Colon-Vargas, Brown University
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

Furthermore, we conducted two distinct variable selection methodologies,
similarly excluding hypertension. Model 6 was based on best subset
selection with 10-fold cross-validation to ascertain the optimal number
of subsets. Notably, for systolic blood pressure, the forward best
subset selection method discerned 13 variables, whereas diastolic blood
pressure exhibited 19 selected variables. However, a limitation inherent
in forward best subset selection is its inability to eliminate
previously selected features, potentially disregarding their relevance
in light of newly added variables. Consequently, this methodology may
yield sub-optimal variable selections due to its lack of adaptability.

>>>>

---
title: "Age modifies the effect of total cholesterol level on systolic blood pressure: Analysis of evidence from the 2015 - 2018 NHANES data"
thanks: "Replication files are available on the author's Github account (http://github.com/okutse/sleepBP). **Current version**: `r format(Sys.time(), '%B %d, %Y')`"
#subtitle: "Short title goes here!"
author:
- Amos Okutse, Brown University
- Monic Colon-Vargas, Brown University
abstract: "**Introduction:** Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec sit amet libero justo. Pellentesque eget nibh ex. Aliquam tincidunt egestas lectus id ullamcorper.

@@

Furthermore, we conducted two distinct variable selection methodologies,
similarly excluding hypertension. Model 6 was based on best subset
selection with 10-fold cross-validation to ascertain the optimal number
of subsets. Best subset selection was selected by identifying the best
model that contains a given number of predictors yielding lowest RSS.
Notably, for systolic blood pressure, the forward best subset selection
method discerned 13 variables, whereas diastolic blood pressure
exhibited 19 selected variables. However, a limitation inherent in
forward best subset selection is its inability to eliminate previously
selected features, potentially disregarding their relevance in light of
newly added variables. Consequently, this methodology may yield
sub-optimal variable selections due to its lack of adaptability.
